---
author: 
  - name          : "Nuria Sagarra"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : "Cristina Lozano-Argüelles"
    affiliation   : "1"
  - name          : "Joseph V. Casillas"
    affilitation  : "1"

affiliation:
  - id            : "1"
    institution   : "Rutgers University"



keywords          : ""
wordcount         : ""

bibliography      : ["r-references.bib"]

floatsintext      : yes
figurelist        : yes
tablelist         : yes
footnotelist      : yes
linenumbers       : yes
mask              : yes
draft             : yes

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_word
---

```{r setup, include = FALSE}
library("papaja")
library("officer")
library("flextable")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r, 'source-scripts-models'}
source(here::here("scripts", "02_load_data.R"))

# Get path to saved models
gca_mods_path  <- here("models", "stress", "s3_adv_int_nat", 
                       "eye_track", "gca")

# Load models as list and store full mod to global env
load(paste0(gca_mods_path, "/ind_mods.Rdata"))
load(paste0(gca_mods_path, "/model_preds.Rdata"))
load(paste0(gca_mods_path, "/full_mods.Rdata"))
load(paste0(gca_mods_path, "/nested_model_comparisons.Rdata"))

```






# BLC article (stress, natives, late advanced learners and interpreters)

## Overview

This document contains updates to the statistical analysis for BLC article 
(3rd revisions). 
Last updated on `r Sys.Date()`. 
The results section can be copied and pasted into the corresponding google doc. 
The tables can also be copy and pasted where appropriate. 

## Main changes

**Participants**  

The updated analysis includes more participants in the interpreter (IN) group 
and a few different participants in the monolingual (M) and advanced learner 
non-interpreter (NIN) groups. 

**Analyses**  

The analysis has been simplified to in 2 major ways: 
by **removing the t-test and GLMM analyses**. 
The motivation behind using the t-tests was to see if participants fixated on 
targets above chance levels (50%) at the offset of the first syllable of the 
target items. 
The problem with this analysis is that is reduced a lot of data to 
approximately 50 data points (and 10ish in the IN group). 
This forced us to run multiple tests and correct for family-wise error using a 
Bonferroni adjustment (and killing our power). 
This was particularly troubling because it was apparent that there was a stress 
effect (oxytones consistently had higher fixation rates), but we refrained 
from testing syllable structure to avoid (1) further correcting alpha and (2) 
harking. 
In place of the t-tests I have included model estimates from the growth curve 
analysis at the target syllable offset ± SE. 
This is not a formal test against chance, but is clearly more reliable than the 
t-tests. 
It also includes the 50ms bin, which I believe will make one of the reviewers 
happy. 
The downside is that it inevitably includes some acoustic information from 
slightly after the initial syllable. 
We don't know how much, but we can examine the time course to see how close 
target fixations are to chance before and after the relevant bin (bin #4, 
4 x 50 = `r 4 * 50` ms). 
With regard to the GLMMs, I believe we can obtain the same information (and 
more) from the GCA. 

## Main findings

The most important change regarding the findings is the **significant effect of 
lexical stress**. 
I believe the power increase due to additional participants is the principle 
explanation for this. 
I was able to get the most complex (maximal) random effects structure to 
converge. 
The story seems to be the following: native speakers anticipate target suffixes 
in all conditions, though certain conditions seem to facilitate processing. 
Specifically, if we consider paroxytone words with open syllables to be the 
default (the most common syllable in Spanish), we see earlier target fixations 
with the addition of the coda and with a shift of stress to the final syllable, 
but the effects are not compounding. 
For example, an unstressed penult is associated more looks to target, but the 
addition of a coda doesn't help that much more. 












# Plots

```{r, 'plot-ind-preds', echo=FALSE, fig.cap="Growth curve estimates of target fixations as a function of lexical stress and syllable structure for each group during the analysis window. Symbols and lines represent model estimates, and the transparent ribbons represents ±SE. Empirical logit values on y-axis correspond to proportions of 0.12, 0.50, 0.88, and 0.98. The horizontal dotted line represents the 50% probability of fixating on the target. The vertical dotted line indicates 200 ms after the offset of the target syllable."}
knitr::include_graphics(
  here("figs", "stress", "s3_adv_int_nat", "eye_track", "stress_p2.png")
)
```

```{r, 'plot-group-preds', echo=FALSE, fig.cap="Growth curve estimates of target fixations as a function of lexical stress and syllable structure for each group during the analysis window. Symbols and lines represent model estimates, and the transparent ribbons represents ±SE. Empirical logit values on y-axis correspond to proportions of 0.12, 0.50, 0.88, and 0.98. The horizontal dotted line represents the 50% probability of fixating on the target. The vertical dotted line indicates 200 ms after the offset of the target syllable."}
knitr::include_graphics(
  here("figs", "stress", "s3_adv_int_nat", "eye_track", "stress_p3.png")
)
```













# Tables 

## Model estimates at target syllable offset  


```{r, table-target-offset-props, eval=T, echo=F}

border_1 <- fp_border(width = 1.5)
border_2 <- fp_border(width = 0.75)

model_preds$target_offset_preds %>% 
  mutate(coda = if_else(coda == 1, "CV", "CVC"), 
         cond = if_else(cond == 1, "Paroxytone", "Oxytone")) %>% 
  arrange(group, desc(cond), coda) %>% 
  mutate(group = blank_same_as_last(as.character(group)), 
         coda =  blank_same_as_last(coda)) %>% 
  select(Group = group, `Lexical stress` = cond, 
         `Syllable structure` = coda, Probability = prob, LB = prob_lb, 
         UB = prob_ub) %>% 
  flextable() %>% 
  width(., j = c(2, 3, 4), width = c(1.1, 1.3, 1.1)) %>% 
  font(., fontname = "Times", part = "all") %>%
  fontsize(., size = 11) %>% 
  border_remove(.) %>%  
  border(., part = "header", 
            border.top = border_1,
            border.bottom = border_2) %>% 
  hline_bottom(., part = "body", border = border_1)
```

*Table 1*: Model estimates for probability of target fixations ±SE at 200 ms 
after the target syllable offset.




## Fixed effects

```{r, warning=F}

top <- ind_mods$gca_mod_ss_int_1 %>% 
  tidy_lme4 %>% 
  mutate(index = c(1, 2, 3, 4, 5, 9, 6, 7, 8, 10, 11, 12, 13, 14)) %>% 
  tibble::rownames_to_column("old_index") %>% 
  arrange(index) %>% 
  mutate(p = format_pval(p), 
         Parameter = fix_param_names(Parameter)) %>% 
  mutate_each(funs(format_fixef_num), Estimate:t) %>% 
  rename(`_t_` = t, `_p_` = p) %>% 
  mutate(frame = "ind", new_index = 1)

my_order <- 
  c(1, 2, 3, 4, 5, 9, 13, 17, 6, 7, 8, 10, 11, 12, 21, 14, 18, 15, 19, 
    16, 20, 22, 23, 24, 25, 29, 26, 30, 27, 31, 28, 32)

bottom <- full_mods$gca_full_mod_int_3 %>% 
  tidy_lme4 %>% 
  mutate(index = my_order) %>% 
  tibble::rownames_to_column("old_index") %>% 
  arrange(index) %>% 
  mutate(p = format_pval(p), 
         Parameter = fix_param_names(Parameter)) %>% 
  mutate_each(funs(format_fixef_num), Estimate:t) %>% 
  rename(`_t_` = t, `_p_` = p) %>% 
  mutate(frame = "full", new_index = if_else(index %in% c(1:12, 21, 22), 0, 1))

pretty_fixed_effects <- 
  bind_rows(top[1:12, ], bottom[13:21, ], top[13:14, ], bottom[23:32, ]) %>% 
  filter(new_index == 1) %>% 
  select(-old_index, -index, -new_index, -frame)


# Include gammas (Gij) after each parameter name
subs <- c(paste0(0:3, 0), paste0(0:3, 1), 
          paste0(0:3, 2), paste0(0:3, 3), 
          paste0(0:3, 4), paste0(0:3, 5), 
          paste0(0:3, 6), paste0(0:3, 7))
var_labels <- parenthesize(paste0(emphasize("&gamma;"), "~", subs, "~"))
pretty_fixed_effects$Parameter %<>% paste(., var_labels)

pretty_fixed_effects %>% 
  select(-effect) %>% 
  knitr::kable(format = "pandoc", align = str_tokenize("lrrrr")) 

```

Appendix 1: Growth curve model fixed effects






## Random effects

```{r, 'ranef-table', results = "asis"}
ranef_table <- full_mods$gca_full_mod_int_3 %>% 
  tidy_ranef_summary %>% 
  # Format the numbers
  mutate_each(funs(format_fixef_num), vcov, sdcor) %>%
  mutate_each(funs(format_cor), -var1, -grp, -vcov, -sdcor) %>%
  sort_ranef_grps %>%
  # Format variable names and group names
  mutate(var1 = fix_param_names(var1) %>% blank_nas,
         grp =  blank_same_as_last(grp) %>% fix_param_names) %>% 
  rename(Group = grp, Parameter = var1, Variance = vcov, SD = sdcor)

# Correlation columns need names with characters so that pandoc can align them
names(ranef_table)[5:10] <- 
  c("Correlations", "&nbsp;", " &nbsp;", "  &nbsp;", "  &nbsp;", "  &nbsp;")

ranef_table %>% 
  knitr::kable(format = "pandoc", align = str_tokenize("llrrrrrr"))
```

Appendix 2: Growth curve model random effects




## Pairwise comparisons

```{r, 'learner-comparison'}
# make table for printing
pairwise_comp <- full_mods$gca_full_mod_int_relevel %>% 
  tidy_lme4 %>% 
  rename(B = Estimate) %>% 
  filter(str_detect(Parameter, "la") == TRUE) %>% 
  select(-effect)

# Add subscript column, convert to rownames, and then add it again
pairwise_comp$subscript <- c(paste0(0:3, 8), paste0(0:3, 9))
pairwise_comp <- tibble::column_to_rownames(pairwise_comp, 'subscript')
pairwise_comp$subscript <- c(paste0(0:3, 8), paste0(0:3, 9))


# Shortcut for inline reporting from the above table
report_pairwise <- function(row_name) report_fixef_row(pairwise_comp, row_name)

```


```{r, pairwise-comp-table, results='asis'}

# Make table for appendix
pretty_pairwise_table <- full_mods$gca_full_mod_int_relevel %>% 
  tidy_lme4 %>% 
  mutate(p = format_pval(p), 
         Parameter = fix_param_names(Parameter)) %>% 
  mutate_each(funs(format_fixef_num), Estimate:t) %>% 
  rename(`_t_` = t, `_p_` = p) %>% 
  filter(str_detect(Parameter, "NIN") == TRUE) %>% 
  select(-effect)

pretty_pairwise_table$Parameter %<>% str_replace("Group NIN", "IN - NIN")

# Include gammas after each parameter name
pw_subs <- c(paste0(0:3, 8), paste0(0:3, 9))
pw_var_labels <- parenthesize(paste0(emphasize("&gamma;"), "~", pw_subs, "~"))
pretty_pairwise_table$Parameter %<>% paste(., pw_var_labels)

pretty_pairwise_table %>% 
  knitr::kable(format = "pandoc", align = str_tokenize("lrrrr")) 

```

Appendix 3: Pairwise comparisons between learner groups. 










# Statistical Analysis

The time course data from the eye-tracking task were analyzed using weighted 
empirical-logit growth curve analysis (GCA, Mirman, 2016). 
We used GCA to model how the probability of fixating on target items changed 
over time and under different suprasegmental and segmental conditions.
We downsampled the data to bins of 50 ms which were centered at the offset of 
the first syllable of target items.
The empirical logit transformation (Barr, 2008) was applied to the binary 
responses (fixations to the target or the distractor). 
<!--
Subsequent analyses focus on the point in the time course 200 ms after the 
target syllable offset (the time required to launch a saccade, Matin, Shao, & 
Boff, 1993). 
-->
The time course of fixation ranged from 200 ms before target syllable offset 
to 600 ms after. 
We chose this window because it captured the portion of the time course in 
which target fixations began to steadily increase from chance. 
The empirical logit transformation (Barr, 2008) was applied to the binary 
responses (fixations to the target or the distractor).
We modeled the time course using linear, quadratic, and cubic orthogonal 
polynomials with fixed effects of group, lexical stress, and syllable 
structure on all time terms.
For the group predictor M was set as the baseline, thus the IN and NIN 
parameters described how the growth curve of the learners differed from that 
of the native controls.
Lexical stress and syllable structure were sum coded such that parameter 
estimates represent effect sizes of change from CV to CVC syllables and 
paroxytone to oxytone stress. 
All models included by-subject random effects on all time terms and the 
syllable structure and lexical stress predictors, as well as by-item random 
effects on all time terms.
Main effects and higher order interactions were assessed using nested model 
comparisons. 
The analysis was conducted in R (R Core Team, 2019) and the GCA models were 
fit using `lme4` (Bates, Mächler, Bolker, & Walker, 2009). 
Pairwise comparisons between learners groups were conducted using the R 
package `multcomp` (Hothorn, Bretz, & Westfall, 2008).

# Results

```{r, 'write-up-prep', warning=F}
# Prepare table to support easy in-line printing of equations
params <- pretty_fixed_effects %>% 
  rename(B = Estimate, t = `_t_`, p = `_p_`)
params$B %<>% str_replace("&minus;", "-")
params$SE %<>% str_replace("&minus;", "-")
params$t %<>% str_replace("&minus;", "-")
params$p %<>% str_replace("< ", "") %>% as.numeric

params$subscript <- 
  c(paste0(0:3, 0), paste0(0:3, 1), 
    paste0(0:3, 2), paste0(0:3, 3), 
    paste0(0:3, 4), paste0(0:3, 5), 
    paste0(0:3, 6), paste0(0:3, 7))

params <- tibble::column_to_rownames(params, 'subscript')

params$subscript <- 
  c(paste0(0:3, 0), paste0(0:3, 1), 
    paste0(0:3, 2), paste0(0:3, 3), 
    paste0(0:3, 4), paste0(0:3, 5), 
    paste0(0:3, 6), paste0(0:3, 7))

# Shortcut for inline reporting from the above table
report_row <- function(row_name) report_fixef_row(params, row_name)

# Pre-calculate intercept as proportion
b0 <- params$B[params$subscript == "00"] %>% as.numeric
b0_prop <- b0 %>% inv_logit %>% round(2) %>% remove_leading_zero

# store int_age_anova as individual object to reduce char count
int_age_anova <- nested_model_comparisons$int_age_anova

```


Figure 1 plots the model estimates from the GCA, and the full model summary is 
available in Appendices 1 and 2. 
We report the results for the M group and then provide comparisons with and 
between the learner groups. 
The model intercept estimates the log odds of M fixating on the target, 
averaging over the time course, lexical stress and syllable structure. 
The log odds were _&gamma;_~00~&nbsp;=&nbsp;`r fixed_digits(b0, 2)` 
(proportion:&nbsp;`r b0_prop`). 
The linear, quadratic, and cubic polynomial time terms captured the sigmoid 
shape of the time course and were retained in the model 
(`r report_row("10")`; `r report_row("20")`; `r report_row("30")`). 


<INSERT FIGURE 1 HERE>  


There was a main effect of lexical stress on the quadratic time term 
(`r pretty_chi_result(nested_model_comparisons$ss_cond_anova, 
"gca_mod_ss_cond_2")`). 
Averaging over syllable structure, a change from paroxytonic (e.g. LAva) to 
oxytonic (e.g. laVÓ) stress decreased the bowing of the trajectory at the 
center of the time course (`r report_row("22")`) indicating that M fixated on 
oxytonic targets earlier than paroxytonic targets.
There was also a main effect of syllable structure on the cubic time term 
(`r pretty_chi_result(nested_model_comparisons$ss_coda_anova, 
"gca_mod_ss_coda_3")`), as well as a syllable structure &times; lexical 
stress interaction on the linear time term 
(`r pretty_chi_result(nested_model_comparisons$ss_int_anova,
"gca_mod_ss_int_1")`), such that the effect of lexical stress decreased the 
overall slope (`r report_row("31")`) and the bowing of the vertices (i.e., 
turning points) of closed, paroxytonic syllables (`r report_row("15")`).
This indicates that M fixated on the paroxytone targets slightly later in the 
time course, whereas they fixated on oxytone targets earlier, but at a slower, 
more steady rate. 
The presence of the coda increased the rate of target fixation on paroxytone 
items, but had little effect on oxytone items (see the upper panels of Figure 
1).

Focusing on the offset of the target syllable, the model estimated target 
fixations above 50% in all conditions 
(Paroxytone CV: `r target_offset_prob(group = "M", coda = 1, cond = 1)`; 
Paroxytone CVC: `r target_offset_prob(group = "M", coda = -1, cond = 1)`; 
Oxytone CV: `r target_offset_prob(group = "M", coda = 1, cond = -1)`; 
Oxytone CVC: `r target_offset_prob(group = "M", coda = -1, cond = -1)`). 
Table 1 provides estimates ±SE for all groups in all conditions. 
Taken together, the analysis indicated that the M group anticipated target 
suffixes in all conditions, though certain conditions seem to facilitate 
prediction. 
Specifically, defaulting from a paroxytone with a CV penult (e.g. LAva), 
one observes earlier target fixations with the addition of a coda and with a 
shift of stress to the final syllable (e.g. firMÓ), suggesting that marked 
sequences facilitate lexical access in native speakers.


<INSERT TABLE 1 HERE>  


With regard to IN and NIN, there was a simple interaction of the quadratic 
time term on the intercept for the NIN group (`r report_row("23")`). 
That is, the NIN had a more bowed trajectory at the offset of the target 
syllable than M, indicating that, overall, NIN fixated on targets later than 
M. 
Additionally, there was a lexical stress &times; syllable structure &times; 
group NIN interaction on the linear slope (`r report_row("16")`), such that 
NIN had a steeper slope than M in CV syllables of paroxytone words.
This indicates that NIN fixated on targets later the default condition 
(i.e., LAva), but earlier in other conditions (i.e., laVÓ, FIRma, firMÓ). 
For the IN group, there was also a simple interaction of the quadratic time
term on the intercept (`r report_row("24")`). 
Thus, with regard to M, IN also fixated later on targets overall. 
Finally, there was a lexical stress &times; syllable structure 
interaction with IN on the cubic time term (`r report_row("37")`), indicative 
of sharper vertices for CV oxytone targets. 
Thus, IN fixated on CV oxytones (i.e., laVÓ) at a faster rate than M, though 
they did so later in the time course. 
IN also showed a lower proportion of target fixations than M 200 ms after the 
target syllable offset (see the upper right panel of Figure 2).


<INSERT FIGURE 2 HERE>  


To sum up, both learner groups showed later target fixations in the default, 
CV paroxytone condition (i.e., LAva).
This assertion is corroborated by examining the NIN and INs' proportion of 
target fixations at the target syllable offset (see Table 1).
Specifically, the model estimates suggest that NIN did not anticipate with CV 
paroxytones (`r target_offset_prob(group = "NIN", coda = 1, cond = 1)`), but 
did so at a higher rate in all other conditions 
(Paroxytone CVC: `r target_offset_prob(group = "NIN", coda = -1, cond = 1)`; 
Oxytone CV: `r target_offset_prob(group = "NIN", coda = 1, cond = -1)`; 
Oxytone CVC: `r target_offset_prob(group = "M", coda = -1, cond = -1)`). 
The same was true for the IN group 
(Paroxytone CV: `r target_offset_prob(group = "IN", coda = 1, cond = 1)`; 
Paroxytone CVC: `r target_offset_prob(group = "IN", coda = -1, cond = 1)`; 
Oxytone CV: `r target_offset_prob(group = "IN", coda = 1, cond = -1)`; 
Oxytone CVC: `r target_offset_prob(group = "IN", coda = -1, cond = -1)`). 
Importantly, pairwise comparisons (see Appendix 3) showed that the learner 
groups also differed from each other.
Specifically, there was a lexical stress &times; syllable structure 
interaction on the linear and cubic time terms
(`r report_pairwise(6)`; `r report_pairwise(8)`, respectively). 
Figure 2 shows that the learners have nearly identical trajectories for CV 
paroxytones.
In all other conditions IN have steeper slopes with more bowed vertices, 
indicating later target fixations with regard to NIN. 
That said, in all conditions the IN group fixated on targets in equal 
proportion to NIN at the offset of the target syllable (the dotted vertical 
lines), suggesting IN fixate on targets later but at a faster rate.^[The range 
of participant ages was wider for IN (see Table 1). 
Specifically, the three groups were comparable regarding minimum age, but the 
max age (76) exceeded that of the other groups. 
To address this possible confound we fit an additional model to the IN data 
including age as a continuous predictor. 
There was no effect of age on the intercept
(`r pretty_chi_result(int_age_anova, "gca_mod_int_age_0")`), nor on any of the 
orthogonal polynomial time terms (Time^1^ &times; Age:
`r pretty_chi_result(int_age_anova, "gca_mod_int_age_1")`; Time^2^ &times; Age: 
`r pretty_chi_result(int_age_anova, "gca_mod_int_age_2")`; Time^3^ &times; Age: 
`r pretty_chi_result(int_age_anova, "gca_mod_int_age_3")`). 
Thus, we found no evidence suggesting that the probability of fixating on 
targets was modulated by age in the IN group, and, to the extent possible, we 
discard the possibility that variations in the time courses of IN and NIN can 
be explained by age-related processing differences.]

